Mbh-n paper

### 2015-08-26 papers/mbhn/mbhn.tex
nature said no

\documentclass[preprint2]{aastex}

\usepackage{natbib}
%\bibliographystyle{apj}
\usepackage{longtable}
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{tabularx}
\usepackage{bm}
%%\graphicspath{{/Users/gsavorgnan/galaxy_vivisection/results/plots/}}

@@

@@

\begin{table*}
\centering
\caption{Linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ diagram.}
\begin{tabular}{llccccc}
\tableline
\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
 & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - \langle MAG_{\rm sph} \rangle)/{\rm mag}]$} \\ [0.5em]
All (62)               & BCES $(Y|X)$               & $-23.88 \pm 0.15$ & $-7.17 \pm 0.80$ & $0.51$ & $-$ & $1.18$ \\
                       & mFITEXY $(Y|X)$            & $-23.95 \pm 0.13$ & $-6.70 \pm 0.45$ & $0.51$ & $0.56^{+0.15}_{-0.10}$ & $0.98$ \\
                       & {\tt linmix\_err} $(Y|X)$  & $-23.92 \pm 0.15$ & $-6.40 \pm 0.57$ & $0.51$ & $0.74 \pm 0.13$ & $1.07$ \\ [0.5em]
                       & BCES $(X|Y)$               & $-23.88 \pm 0.14$ & $-6.70 \pm 0.51$ & $0.51$ & $-$ & $1.11$ \\
                       & mFITEXY $(X|Y)$            & $-23.94 \pm 0.14$ & $-7.50 \pm 0.52$ & $0.51$ & $0.59^{+0.17}_{-0.11}$ & $1.23$ \\
                       & {\tt linmix\_err} $(X|Y)$  & $-23.94 \pm 0.16$ & $-7.51 \pm 0.62$ & $0.51$ & $0.81 \pm 0.16$ & $1.23$ \\ [0.5em]
                       & BCES Bisector              & $-23.88 \pm 0.14$ & $-6.93 \pm 0.60$ & $0.51$ & $-$ & $1.14$ \\
                       & mFITEXY Bisector           & $-23.94 \pm 0.13$ & $-7.08 \pm 0.34$ & $0.51$ & $-$ & $1.16$ \\
                       & {\tt linmix\_err} Bisector & $-23.93 \pm 0.16$ & $-6.91 \pm 0.42$ & $0.51$ & $-$ & $1.14$ \\ [0.5em]

@@

Bulges (30)	       & BCES $(Y|X)$		    & $-22.25 \pm 0.20$ & $-5.88 \pm 3.06$ & $0.26$ & $-$ & $1.16$ \\
		       & mFITEXY $(Y|X)$	    & $-22.19 \pm 0.14$ & $-2.99 \pm 0.73$ & $0.26$ & $0.52^{+0.18}_{-0.10}$ & $0.75$ \\
		       & {\tt linmix\_err} $(Y|X)$  & $-22.20 \pm 0.17$ & $-2.48 \pm 1.21$ & $0.26$ & $0.67 \pm 0.15$ & $0.83$ \\ [0.5em]
		       & BCES $(X|Y)$		    & $-22.25 \pm 0.20$ & $-5.85 \pm 1.83$ & $0.26$ & $-$ & $1.15$ \\
		       & mFITEXY $(X|Y)$	    & $-22.17 \pm 0.25$ & $-7.65 \pm 2.43$ & $0.26$ & $0.87^{+0.30}_{-0.18}$ & $1.46$ \\
		       & {\tt linmix\_err} $(X|Y)$  & $-22.16 \pm 0.31$ & $-7.80 \pm 3.89$ & $0.26$ & $1.18 \pm 0.65$ & $1.48$ \\ [0.5em]
		       & BCES Bisector  	    & $-22.25 \pm 0.20$ & $-5.87 \pm 2.06$ & $0.26$ & $-$ & $1.16$ \\
		       & mFITEXY Bisector	    & $-22.18 \pm 0.20$ & $-4.34 \pm 0.84$ & $0.26$ & $-$ & $0.96$ \\
		       & {\tt linmix\_err} Bisector & $-22.19 \pm 0.25$ & $-3.83 \pm 1.39$ & $0.26$ & $-$ & $0.91$ \\ [0.5em]

@@

\tableline 
\tableline
\end{tabular}
\label{tab:lregsph} 
\tablecomments{For each subsample, we indicate $\langle MAG_{\rm sph} \rangle$, its average value of spheroid magnitudes. 
In the last two columns, we report $\epsilon$, the intrinsic scatter, and $\Delta$, the total rms scatter in the $\log(M_{\rm BH})$ direction. 
Both the early- and late-type subsamples do not contain the two galaxies classified as S0/Sp and the two galaxies classified as mergers (45+17=66-2-2). }
\end{table*}

>>>>

\documentclass[preprint2]{emulateapj}

\usepackage{natbib}
\bibliographystyle{apj}
\usepackage{longtable}
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{tabularx}
\usepackage{bm}
\usepackage{color}
\usepackage{hyperref}

@@

\section{Data}

\input{table_sample.tex}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mag_vs_n_maj.pdf}
\caption{}
\label{fig:magn}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_n_maj.pdf}
\caption{}
\label{fig:mbhn}
\end{center}
\end{figure}

\begin{table*}
\centering
\caption{Linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ diagram.}
\begin{tabular}{llccccc}
\tableline
\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
 & \multicolumn{6}{l}{$MAG_{\rm sph}/{\rm [mag]} = \alpha + \beta \bigl(\log n_{\rm sph} - \langle \log n_{\rm sph,maj} \rangle \bigr)$} \\ [0.5em]
All (62)               & BCES $(Y|X)$               & $-23.88 \pm 0.15$ & $-7.17 \pm 0.80$ & $0.51$ & $-$ & $1.18$ \\
                       & mFITEXY $(Y|X)$            & $-23.95 \pm 0.13$ & $-6.70 \pm 0.45$ & $0.51$ & $0.56^{+0.15}_{-0.10}$ & $0.98$ \\
                       & {\tt linmix\_err} $(Y|X)$  & $-23.92 \pm 0.15$ & $-6.40 \pm 0.57$ & $0.51$ & $0.74 \pm 0.13$ & $1.07$ \\ [0.5em]
                       & BCES $(X|Y)$               & $-23.88 \pm 0.14$ & $-6.70 \pm 0.51$ & $0.51$ & $-$ & $1.11$ \\
                       & mFITEXY $(X|Y)$            & $-23.94 \pm 0.14$ & $-7.50 \pm 0.52$ & $0.51$ & $0.59^{+0.17}_{-0.11}$ & $1.23$ \\
                       & {\tt linmix\_err} $(X|Y)$  & $-23.94 \pm 0.16$ & $-7.51 \pm 0.62$ & $0.51$ & $0.81 \pm 0.16$ & $1.23$ \\ [0.5em]
                       & BCES Bisector              & $-23.88 \pm 0.14$ & $-6.93 \pm 0.60$ & $0.51$ & $-$ & $1.14$ \\
                       & mFITEXY Bisector           & $-23.94 \pm 0.13$ & $-7.08 \pm 0.34$ & $0.51$ & $-$ & $1.16$ \\
                       & {\tt linmix\_err} Bisector & $-23.93 \pm 0.16$ & $-6.91 \pm 0.42$ & $0.51$ & $-$ & $1.14$ \\ [0.5em]

@@

Bulge  (30)	       & BCES $(Y|X)$		    & $-22.25 \pm 0.20$ & $-5.88 \pm 3.06$ & $0.26$ & $-$ & $1.16$ \\
		       & mFITEXY $(Y|X)$	    & $-22.19 \pm 0.14$ & $-2.99 \pm 0.73$ & $0.26$ & $0.52^{+0.18}_{-0.10}$ & $0.75$ \\
		       & {\tt linmix\_err} $(Y|X)$  & $-22.20 \pm 0.17$ & $-2.48 \pm 1.21$ & $0.26$ & $0.67 \pm 0.15$ & $0.83$ \\ [0.5em]
		       & BCES $(X|Y)$		    & $-22.25 \pm 0.20$ & $-5.85 \pm 1.83$ & $0.26$ & $-$ & $1.15$ \\
		       & mFITEXY $(X|Y)$	    & $-22.17 \pm 0.25$ & $-7.65 \pm 2.43$ & $0.26$ & $0.87^{+0.30}_{-0.18}$ & $1.46$ \\
		       & {\tt linmix\_err} $(X|Y)$  & $-22.16 \pm 0.31$ & $-7.80 \pm 3.89$ & $0.26$ & $1.18 \pm 0.65$ & $1.48$ \\ [0.5em]
		       & BCES Bisector  	    & $-22.25 \pm 0.20$ & $-5.87 \pm 2.06$ & $0.26$ & $-$ & $1.16$ \\
		       & mFITEXY Bisector	    & $-22.18 \pm 0.20$ & $-4.34 \pm 0.84$ & $0.26$ & $-$ & $0.96$ \\
		       & {\tt linmix\_err} Bisector & $-22.19 \pm 0.25$ & $-3.83 \pm 1.39$ & $0.26$ & $-$ & $0.91$ \\ [1.0em]

% & \multicolumn{6}{l}{$MAG_{\rm sph}/{\rm [mag]} = \alpha + \beta \bigl(\log n_{\rm sph,eq} - \langle \log n_{\rm sph,eq} \rangle \bigr)$} \\ [0.5em]
%
% All (62)		 & BCES $(Y|X)$ 	      & $-23.88 \pm 0.15$ & $-7.04 \pm 0.89$ & $0.50$ & $-$ & $1.19$ \\
%			 & mFITEXY $(Y|X)$	      & $-23.95 \pm 0.12$ & $-6.43 \pm 0.41$ & $0.50$ & $0.55^{+0.16}_{-0.10}$ & $0.96$ \\
%			 & {\tt linmix\_err} $(Y|X)$  & $-23.91 \pm 0.14$ & $-6.04 \pm 0.54$ & $0.50$ & $0.75 \pm 0.13$ & $1.07$ \\ [0.5em]
%			 & BCES $(X|Y)$ 	      & $-23.88 \pm 0.14$ & $-6.73 \pm 0.48$ & $0.50$ & $-$ & $1.14$ \\
%			 & mFITEXY $(X|Y)$	      & $-23.93 \pm 0.13$ & $-7.13 \pm 0.48$ & $0.50$ & $0.58^{+0.17}_{-0.12}$ & $1.21$ \\
%			 & {\tt linmix\_err} $(X|Y)$  & $-23.93 \pm 0.15$ & $-7.14 \pm 0.57$ & $0.50$ & $0.76 \pm 0.16$ & $1.21$ \\ [0.5em]
%			 & BCES Bisector	      & $-23.88 \pm 0.15$ & $-6.88 \pm 0.62$ & $0.50$ & $-$ & $1.17$ \\
%			 & mFITEXY Bisector	      & $-23.94 \pm 0.13$ & $-6.76 \pm 0.31$ & $0.50$ & $-$ & $1.15$ \\
%			 & {\tt linmix\_err} Bisector & $-23.92 \pm 0.15$ & $-6.55 \pm 0.40$ & $0.50$ & $-$ & $1.12$ \\ [0.5em]
%
%
% Elliptical (30)	 & BCES $(Y|X)$ 	      & $-25.46 \pm 0.26$ & $4.92 \pm 4.72$ & $0.77$ & $-$ & $1.46$ \\
%			 & mFITEXY $(Y|X)$	      & $-25.66 \pm 0.24$ & $-12.65 \pm 2.78$ & $0.77$ & $0.42^{+0.38}_{-0.42}$ & $1.27$ \\
%			 & {\tt linmix\_err} $(Y|X)$  & $-25.55 \pm 0.26$ & $-8.54 \pm 4.68$ & $0.77$ & $0.80 \pm 0.24$ & $1.20$ \\ [0.5em]
%			 & BCES $(X|Y)$ 	      & $-25.46 \pm 0.40$ & $-20.83 \pm 11.31$ & $0.77$ & $-$ & $2.26$ \\
%			 & mFITEXY $(X|Y)$	      & $-25.63 \pm 0.31$ & $-16.13 \pm 4.37$ & $0.77$ & $0.48^{+0.48}_{-0.48}$ & $1.80$ \\
%			 & {\tt linmix\_err} $(X|Y)$  & $-25.63 \pm 0.43$ & $-16.66 \pm 6.50$ & $0.77$ & $1.22 \pm 0.65$ & $1.85$ \\ [0.5em]
%			 & BCES Bisector	      & $-25.46 \pm 0.20$ & $-0.08 \pm 0.10$ & $0.77$ & $-$ & $1.14$ \\
%			 & mFITEXY Bisector	      & $-25.65 \pm 0.28$ & $-14.18 \pm 2.43$ & $0.77$ & $-$ & $1.63$ \\
%			 & {\tt linmix\_err} Bisector & $-25.58 \pm 0.35$ & $-11.30 \pm 4.34$ & $0.77$ & $-$ & $1.38$ \\ [0.5em]
%
%\tableline 
%\tableline
%\end{tabular}
%\end{table*}
%
%\begin{table*}
%\centering
%\caption{Linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ diagram.}
%\begin{tabular}{llccccc}
%\tableline
%\tableline
%{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
%\tableline 
%\\
%
% Lenticular (11)	 & BCES $(Y|X)$ 	      & $-22.08 \pm 0.89$ & $16.29 \pm 24.44$ & $0.29$ & $-$ & $3.25$ \\
%			 & mFITEXY $(Y|X)$	      & $-22.16 \pm 0.20$ & $-5.84 \pm 1.83$ & $0.29$ & $0.31^{+0.28}_{-0.20}$ & $0.61$ \\
%			 & {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $0.29$ & $$ & $$ \\ [0.5em]
%			 & BCES $(X|Y)$ 	      & $-22.08 \pm 0.20$ & $-7.40 \pm 1.27$ & $0.29$ & $-$ & $0.72$ \\
%			 & mFITEXY $(X|Y)$	      & $-22.11 \pm 0.28$ & $-8.30 \pm 3.33$ & $0.29$ & $0.40^{+0.33}_{-0.35}$ & $0.77$ \\
%			 & {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $0.29$ & $$ & $$ \\ [0.5em]
%			 & BCES Bisector	      & $-22.08 \pm 0.30$ & $0.04 \pm 0.05$ & $0.29$ & $-$ & $1.08$ \\
%			 & mFITEXY Bisector	      & $-22.14 \pm 0.25$ & $-6.86 \pm 1.70$ & $0.29$ & $-$ & $0.70$ \\
%			 & {\tt linmix\_err} Bisector & $$ & $$ & $0.29$ & $$ & $$ \\ [0.5em]
%
%
% Spiral (17)		 & BCES $(Y|X)$ 	      & $-22.33 \pm 0.62$ & $-14.53 \pm 71.43$ & $0.17$ & $-$ & $2.71$ \\
%			 & mFITEXY $(Y|X)$	      & $-22.37 \pm 0.27$ & $-6.53 \pm 2.84$ & $0.17$ & $0.47^{+0.52}_{-0.39}$ & $0.95$ \\
%			 & {\tt linmix\_err} $(Y|X)$  & $-22.35 \pm 1.23$ & $-3.62 \pm 21.94$ & $0.17$ & $0.63 \pm 0.25$ & $0.93$ \\ [0.5em]
%			 & BCES $(X|Y)$ 	      & $-22.33 \pm 0.35$ & $-7.91 \pm 5.53$ & $0.17$ & $-$ & $1.54$ \\
%			 & mFITEXY $(X|Y)$	      & $-22.74 \pm 0.56$ & $-14.91 \pm 10.03$ & $0.17$ & $0.65^{+1.41}_{-0.65}$ & $2.82$ \\
%			 & {\tt linmix\_err} $(X|Y)$  & $-22.66 \pm 0.88$ & $-16.17 \pm 21.34$ & $0.17$ & $1.47 \pm 2.15$ & $3.04$ \\ [0.5em]
%			 & BCES Bisector	      & $-22.33 \pm 0.44$ & $-10.25 \pm 18.84$ & $0.17$ & $-$ & $1.94$ \\
%			 & mFITEXY Bisector	      & $-22.48 \pm 0.44$ & $-9.10 \pm 3.31$ & $0.17$ & $-$ & $1.75$ \\
%			 & {\tt linmix\_err} Bisector & $-22.41 \pm 1.07$ & $-5.98 \pm 28.65$ & $0.17$ & $-$ & $1.24$ \\ [0.5em]
%
%
% Early-type (43)	 & BCES $(Y|X)$ 	      & $-24.55 \pm 0.22$ & $-10.81 \pm 1.96$ & $0.64$ & $-$ & $1.46$ \\
%			 & mFITEXY $(Y|X)$	      & $-24.70 \pm 0.14$ & $-7.89 \pm 0.63$ & $0.64$ & $0.46^{+0.18}_{-0.14}$ & $0.93$ \\
%			 & {\tt linmix\_err} $(Y|X)$  & $-24.63 \pm 0.18$ & $-7.34 \pm 0.83$ & $0.64$ & $0.75 \pm 0.16$ & $1.02$ \\ [0.5em]
%			 & BCES $(X|Y)$ 	      & $-24.55 \pm 0.16$ & $-8.35 \pm 0.68$ & $0.64$ & $-$ & $1.10$ \\
%			 & mFITEXY $(X|Y)$	      & $-24.69 \pm 0.16$ & $-8.65 \pm 0.73$ & $0.64$ & $0.48^{+0.20}_{-0.15}$ & $1.14$ \\
%			 & {\tt linmix\_err} $(X|Y)$  & $-24.68 \pm 0.20$ & $-8.68 \pm 0.91$ & $0.64$ & $0.77 \pm 0.20$ & $1.14$ \\ [0.5em]
%			 & BCES Bisector	      & $-24.55 \pm 0.18$ & $-9.42 \pm 1.00$ & $0.64$ & $-$ & $1.23$ \\
%			 & mFITEXY Bisector	      & $-24.69 \pm 0.15$ & $-8.25 \pm 0.48$ & $0.64$ & $-$ & $1.10$ \\
%			 & {\tt linmix\_err} Bisector & $-24.65 \pm 0.19$ & $-7.96 \pm 0.62$ & $0.64$ & $-$ & $1.07$ \\ [0.5em]
%
%
% Bulge (30)		 & BCES $(Y|X)$ 	      & $-22.25 \pm 0.50$ & $-16.91 \pm 33.45$ & $0.23$ & $-$ & $2.85$ \\
%			 & mFITEXY $(Y|X)$	      & $-22.21 \pm 0.14$ & $-4.25 \pm 0.94$ & $0.23$ & $0.45^{+0.21}_{-0.13}$ & $0.75$ \\
%			 & {\tt linmix\_err} $(Y|X)$  & $-22.23 \pm 0.17$ & $-3.36 \pm 1.62$ & $0.23$ & $0.61 \pm 0.17$ & $0.87$ \\ [0.5em]
%			 & BCES $(X|Y)$ 	      & $-22.25 \pm 0.23$ & $-7.56 \pm 1.94$ & $0.23$ & $-$ & $1.30$ \\
%			 & mFITEXY $(X|Y)$	      & $-22.23 \pm 0.22$ & $-8.20 \pm 2.44$ & $0.23$ & $0.63^{+0.31}_{-0.19}$ & $1.39$ \\
%			 & {\tt linmix\_err} $(X|Y)$  & $-22.22 \pm 0.28$ & $-8.42 \pm 4.00$ & $0.23$ & $0.96 \pm 0.54$ & $1.43$ \\ [0.5em]
%			 & BCES Bisector	      & $-22.25 \pm 0.31$ & $-10.46 \pm 7.05$ & $0.23$ & $-$ & $1.75$ \\
%			 & mFITEXY Bisector	      & $-22.22 \pm 0.19$ & $-5.62 \pm 0.99$ & $0.23$ & $-$ & $1.05$ \\
%			 & {\tt linmix\_err} Bisector & $-22.23 \pm 0.23$ & $-4.84 \pm 1.75$ & $0.23$ & $-$ & $0.98$ \\ [0.5em]

@@

\tableline 
\tableline
\end{tabular}
\label{tab:lregLn} 
\tablecomments{For each subsample, we indicate $\langle \log n_{\rm sph} \rangle$, its average value of spheroid S\'ersic index. 
In the last two columns, we report $\epsilon$, the intrinsic scatter, and $\Delta$, the total rms scatter in the $L_{\rm sph}$ direction. 
all - mergers - outliers
Both the early- and late-type subsamples do not contain the two galaxies classified as S0/Sp and the two galaxies classified as mergers (45+17=66-2-2). }
\end{table*}

\begin{table*}
\centering
\caption{Linear regression analysis of the $M_{\rm BH} - n_{\rm sph}$ diagram.}
\begin{tabular}{llccccc}
\tableline
\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
 & \multicolumn{6}{l}{$\log \bigl( M_{\rm BH}/{\rm [M_\odot]} \bigr) = \alpha + \beta \bigl(\log n_{\rm sph} - \langle \log n_{\rm sph} \rangle \bigr)$} \\ [0.5em]
 All (62)		& BCES $(Y|X)$  	     & $8.14 \pm 0.08$ & $3.56 \pm 0.38$ & $0.51$ & $-$ & $0.60$ \\
 			& mFITEXY $(Y|X)$	     & $8.18 \pm 0.06$ & $3.27 \pm 0.21$ & $0.51$ & $0.22^{+0.10}_{-0.07}$ & $0.45$ \\
 			& {\tt linmix\_err} $(Y|X)$  & $8.17 \pm 0.06$ & $3.17 \pm 0.24$ & $0.51$ & $0.29 \pm 0.07$ & $0.56$ \\ [0.5em]
 			& BCES $(X|Y)$  	     & $8.14 \pm 0.08$ & $3.56 \pm 0.25$ & $0.51$ & $-$ & $0.60$ \\
 			& mFITEXY $(X|Y)$	     & $8.18 \pm 0.06$ & $3.51 \pm 0.23$ & $0.51$ & $0.23^{+0.10}_{-0.07}$ & $0.60$ \\
 			& {\tt linmix\_err} $(X|Y)$  & $8.17 \pm 0.07$ & $3.49 \pm 0.26$ & $0.51$ & $0.30 \pm 0.07$ & $0.60$ \\ [0.5em]
 			& BCES Bisector 	     & $8.14 \pm 0.08$ & $3.56 \pm 0.29$ & $0.51$ & $-$ & $0.60$ \\
 			& mFITEXY Bisector	     & $8.18 \pm 0.06$ & $3.39 \pm 0.15$ & $0.51$ & $-$ & $0.58$ \\
 			& {\tt linmix\_err} Bisector & $8.17 \pm 0.07$ & $3.33 \pm 0.18$ & $0.51$ & $-$ & $0.57$ \\ [0.5em]

 Elliptical (30)	& BCES $(Y|X)$  	     & $8.80 \pm 0.53$ & $-18.16 \pm 53.99$ & $0.76$ & $-$ & $3.02$ \\
 			& mFITEXY $(Y|X)$	     & $8.90 \pm 0.10$ & $4.47 \pm 0.88$ & $0.76$ & $0.29^{+0.14}_{-0.10}$ & $0.56$ \\
 			& {\tt linmix\_err} $(Y|X)$  & $8.84 \pm 0.12$ & $3.56 \pm 1.35$ & $0.76$ & $0.44 \pm 0.12$ & $0.59$ \\ [0.5em]
 			& BCES $(X|Y)$  	     & $8.80 \pm 0.18$ & $8.00 \pm 2.55$ & $0.76$ & $-$ & $1.01$ \\
 			& mFITEXY $(X|Y)$	     & $8.92 \pm 0.15$ & $6.85 \pm 1.75$ & $0.76$ & $0.36^{+0.20}_{-0.15}$ & $0.89$ \\
 			& {\tt linmix\_err} $(X|Y)$  & $8.89 \pm 0.20$ & $6.96 \pm 2.49$ & $0.76$ & $0.63 \pm 0.30$ & $0.89$ \\ [0.5em]
 			& BCES Bisector 	     & $8.80 \pm 0.11$ & $-0.03 \pm 0.10$ & $0.76$ & $-$ & $0.64$ \\
 			& mFITEXY Bisector	     & $8.91 \pm 0.13$ & $5.42 \pm 0.85$ & $0.76$ & $-$ & $0.73$ \\
 			& {\tt linmix\_err} Bisector & $8.85 \pm 0.16$ & $4.73 \pm 1.30$ & $0.76$ & $-$ & $0.67$ \\ [0.5em]

 Lenticular (11)	& BCES $(Y|X)$  	     & $7.75 \pm 0.58$ & $-11.51 \pm 31.78$ & $0.33$ & $-$ & $2.11$ \\
 			& mFITEXY $(Y|X)$	     & $7.65 \pm 0.12$ & $3.78 \pm 1.20$ & $0.33$ & $0.00^{+0.00}_{-0.00}$ & $0.26$ \\
 			& {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $0.33$ & $$ & $$ \\ [0.5em]
 			& BCES $(X|Y)$  	     & $7.75 \pm 0.13$ & $3.54 \pm 0.99$ & $0.33$ & $-$ & $0.46$ \\
 			& mFITEXY $(X|Y)$	     & $7.65 \pm 0.12$ & $3.78 \pm 1.20$ & $0.33$ & $0.00^{+0.00}_{-0.00}$ & $0.49$ \\
 			& {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $0.33$ & $$ & $$ \\ [0.5em]
 			& BCES Bisector 	     & $7.75 \pm 0.13$ & $-0.09 \pm 0.15$ & $0.33$ & $-$ & $0.48$ \\
 			& mFITEXY Bisector	     & $7.65 \pm 0.12$ & $3.78 \pm 0.85$ & $0.33$ & $-$ & $0.49$ \\
 			& {\tt linmix\_err} Bisector & $$ & $$ & $0.33$ & $-$ & $$ \\ [0.5em]

 Spiral (17)		& BCES $(Y|X)$  	     & $7.18 \pm 0.28$ & $6.78 \pm 6.62$ & $0.18$ & $-$ & $1.23$ \\
 			& mFITEXY $(Y|X)$	     & $7.24 \pm 0.13$ & $4.48 \pm 0.90$ & $0.18$ & $0.13^{+0.42}_{-0.13}$ & $0.52$ \\
 			& {\tt linmix\_err} $(Y|X)$  & $7.22 \pm 0.16$ & $3.57 \pm 1.36$ & $0.18$ & $0.39 \pm 0.19$ & $0.70$ \\ [0.5em]
 			& BCES $(X|Y)$  	     & $7.18 \pm 0.23$ & $5.48 \pm 1.93$ & $0.18$ & $-$ & $0.99$ \\
 			& mFITEXY $(X|Y)$	     & $7.24 \pm 0.14$ & $4.62 \pm 0.96$ & $0.18$ & $0.13^{+0.43}_{-0.13}$ & $0.85$ \\
 			& {\tt linmix\_err} $(X|Y)$  & $7.21 \pm 0.21$ & $4.86 \pm 1.64$ & $0.18$ & $0.45 \pm 0.31$ & $0.89$ \\ [0.5em]
 			& BCES Bisector 	     & $7.18 \pm 0.25$ & $6.06 \pm 3.66$ & $0.18$ & $-$ & $1.10$ \\
 			& mFITEXY Bisector	     & $7.24 \pm 0.14$ & $4.55 \pm 0.66$ & $0.18$ & $-$ & $0.84$ \\
 			& {\tt linmix\_err} Bisector & $7.22 \pm 0.19$ & $4.12 \pm 1.07$ & $0.18$ & $-$ & $0.77$ \\ [0.5em]

 Early-type (43)	& BCES $(Y|X)$  	     & $8.54 \pm 0.10$ & $4.07 \pm 0.87$ & $0.64$ & $-$ & $0.65$ \\
 			& mFITEXY $(Y|X)$	     & $8.58 \pm 0.07$ & $3.32 \pm 0.34$ & $0.64$ & $0.24^{+0.10}_{-0.07}$ & $0.45$ \\
 			& {\tt linmix\_err} $(Y|X)$  & $8.57 \pm 0.08$ & $3.12 \pm 0.43$ & $0.64$ & $0.32 \pm 0.08$ & $0.53$ \\ [0.5em]
 			& BCES $(X|Y)$  	     & $8.54 \pm 0.09$ & $3.95 \pm 0.55$ & $0.64$ & $-$ & $0.63$ \\
 			& mFITEXY $(X|Y)$	     & $8.59 \pm 0.08$ & $3.88 \pm 0.43$ & $0.64$ & $0.26^{+0.11}_{-0.08}$ & $0.62$ \\
 			& {\tt linmix\_err} $(X|Y)$  & $8.59 \pm 0.09$ & $3.82 \pm 0.50$ & $0.64$ & $0.35 \pm 0.10$ & $0.61$ \\ [0.5em]
 			& BCES Bisector 	     & $8.54 \pm 0.10$ & $4.01 \pm 0.63$ & $0.64$ & $-$ & $0.64$ \\
 			& mFITEXY Bisector	     & $8.59 \pm 0.07$ & $3.58 \pm 0.27$ & $0.64$ & $-$ & $0.58$ \\
 			& {\tt linmix\_err} Bisector & $8.58 \pm 0.08$ & $3.44 \pm 0.33$ & $0.64$ & $-$ & $0.56$ \\ [0.5em]

\tableline 
\tableline
\end{tabular}
\label{tab:lregMn} 
\tablecomments{For each subsample, we indicate $\langle \log n_{\rm sph} \rangle$, its average value of spheroid S\'ersic index. 
In the last two columns, we report $\epsilon$, the intrinsic scatter, and $\Delta$, the total rms scatter in the $L_{\rm sph}$ direction. 
all - mergers - outliers
Both the early- and late-type subsamples do not contain the two galaxies classified as S0/Sp and the two galaxies classified as mergers (45+17=66-2-2).  }
\end{table*}
